Dynamical modeling of tidal streams

### 2013-12-06 tex/ms.tex
streams: add times figures to ms
streams: add vlos
streams: add plots as a function of angle along the stream

\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lb.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_ld.ps}
  \caption{}\label{fig:gd1_lbd}
%python plot_stream.py ../tex/gd1_evol_lb.ps
%python plot_stream.py ../tex/gd1_evol_ld.ps
\end{figure}

@@

>>>>

\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lb.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_ld.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lvlos.ps}
  \caption{}\label{fig:gd1_lbd}
%python plot_stream.py ../tex/gd1_evol_lb.ps
%python plot_stream.py ../tex/gd1_evol_ld.ps
%python plot_stream.py ../tex/gd1_evol_lvlos.ps
\end{figure}

@@

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_timeshist.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_timesdO.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_timesda.ps}
  \caption{}\label{fig:gd1_times}
%python plot_stream.py ../tex/gd1_evol_timeshist.ps
%python plot_stream.py ../tex/gd1_evol_timesdO.ps
%python plot_stream.py ../tex/gd1_evol_timesda.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aadohist.ps}
  \caption{}\label{fig:gd1_dohist}
%python plot_stream.py ../tex/gd1_evol_aadohist.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaaparopar.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaaparoperp.ps}\\
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaaparaperp.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaapartime.ps}
  \caption{}\label{fig:gd1_apar}
%python plot_stream.py ../tex/gd1_evol_aaaparopar.ps
%python plot_stream.py ../tex/gd1_evol_aaaparoperp.ps
%python plot_stream.py ../tex/gd1_evol_aaaparaperp.ps
%python plot_stream.py ../tex/gd1_evol_aaapartime.ps
\end{figure}
